Supplementary Information

### 2021-02-08 doc/manuscript/MEE_manuscript.Rmd
checked new results (no updates)
#111

```{r , eval=FALSE, echo=FALSE}
## Tallies for the following paragraph (Jan 12)
#sameV_sameW: LDWp, NMt,NMp, NIOt, NIOp, SCBIp,  ZOFp,ZOFt,  (8)
#sameV_diffW: BCNMp, BCNMt, HFt, HKKp, LDWt,  SCBIt, SCp,SCt,  CBp, CBt (10)
#diffV_diffW: HFp, HKKt
```
The three metrics of growth ($RW$, $BAI$, and $\Delta AGB$)  exhibited similar strength of correlation and direction of response to climate variables across the range of potential time windows, but the optimal time window or even the top climate variable sometimes differed (Figs. `r all_climwin`).
In 8 of 20 cases, both the optimal climate variable and time window were identical across growth metrics (e.g., Fig. `r climwin_sameV_sameW`). 
In 10 cases, *climwin* identified the same climate variable but different (often overlapping) time windows (e.g., Fig. `r climwin_sameV_diffW`). 
Finally, in two cases of variables that had only weak effects and mixed responses among species in the final models (temperature variable group at HKK, precipitation variable group at HF; Figs. `r clim_sens`, `r GLS_HKK`, `r GLS_HF`), *climwin* identified different climate variables and different time windows (e.g., Fig. `r climwin_diffV_diffW`). 
Henceforth, unless otherwise noted, we focus on the climate sensitivities identified with $RW$ as the growth metric and for the full set of cores (*i.e.*, including those for which $DBH$ could not be reconstructed).

```{r , eval=FALSE, echo=FALSE}
## Tallies for the paragraph below (as of Jan 12)
#BCNM: 1 species with both, 2 with just P
#HKK: 3 species with both, 1 with just T (CHTA)
#SCBI: 11 species with both, 3 with just P (FRNI, FAGR, PIST)
#LDW:  4 species with both,  2  with just P (ACSA, CAOV)
#HF:  4 species with both
#ZOF:  3 species with both
#NIO:  1 species with both
#LT:  2 species with both
#CB:  8 species with both
#SC:  1 species with both
```
Within the context of the GLS model, which tested for first- and negative second- order linear effects of both a precipitation and a temperature variable, both a precipitation and a temperature variable were included in the top model for 80% of site-species combinations (n=37 of 46; Fig. `r clim_sens`). 
There were seven site-species combinations for which only a precipitation term was significant (2 at BCNM, 3 at SCBI, and 2 at LDW), one for which only a temperature term was significant (*Chukrasia tabularis* at HKK), and none with no significant climate responses. 
Precipitation and temperature variables were rarely influential over the same time window (exception: LDW).
Below, we summarize the precipitation and temperature variables included in these models and their direction of response.

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan12)

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan12)
n_spst_DBH_analyzed= 43 # n species with DBH analyzed: 43 (45 - 2: 2 Hansley)
n_spst_RW_DBH_sig=35 #  species with sig first-order linear DBH term
n_spst_RW_DBH_2nd_order=26
n_spst_RW_DBH_2nd_order_neg=21
n_spst_BAI_DBH_best_model=42 #exception: ACRU at HF  
n_spst_BAI_DBH_best_model_pos=40 #exceptions: PIPO at LT (reconstructed DBH down to only 15cm) and PILO at CB (short DBH range on old trees), both neg but not significant
n_spst_BAI_DBH_best_model_2nd=41
n_spst_BAI_DBH_best_model_2nd_neg=40 # exception: PILO at CB
n_spst_dAGB_DBH_best_model=42 # exception: PILO at CB
```

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_DBHx_analyzed=204 #n rows in climate_interactions_coefficients, excluding Hansley
n_DBHx_analyzed_sig=88
#precip:
n_DBHxP_RW_analyzed= 36
n_DBHxP_RW_sig=16
n_DBHxP_RW_sig_pos=n_DBHxP_RW_sig-4 #(exceptions: BEAL, TSCA, ACRU at HF, AFXY at HKK*) *pos response to precip in current growing season

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan12)
n_tested=37 #same for all metrics
n_best_model_RW=30
n_best_model_BAI=32
n_best_model_AGB=30
n_best_model_neg_RW=n_best_model_RW-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB)  90%
n_best_model_neg_BAI=n_best_model_BAI-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90.6%
n_best_model_neg_AGB=n_best_model_AGB-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90%
percent_neg_of_sig_trends="90-91%"
percent_sig_neg_trend_of_analyzed = "73-78%" 
#species consistently independent of year: PIEN and PILO at CB, CHTA at HKK, PIST3 at NM,

>>>>

```{r , eval=FALSE, echo=FALSE}
## Tallies for the following paragraph (Feb 8)
#sameV_sameW: LDWp, NMt,NMp, NIOt, NIOp, SCBIp,  ZOFp,ZOFt,  (8)
#sameV_diffW: BCNMp, BCNMt, HFt, HKKp, LDWt,  SCBIt, SCp,SCt,  CBp, CBt (10)
#diffV_diffW: HFp, HKKt
```
The three metrics of growth ($RW$, $BAI$, and $\Delta AGB$)  exhibited similar strength of correlation and direction of response to climate variables across the range of potential time windows, but the optimal time window or even the top climate variable sometimes differed (Figs. `r all_climwin`).
In 8 of 20 cases, both the optimal climate variable and time window were identical across growth metrics (e.g., Fig. `r climwin_sameV_sameW`). 
In 10 cases, *climwin* identified the same climate variable but different (often overlapping) time windows (e.g., Fig. `r climwin_sameV_diffW`). 
Finally, in two cases of variables that had only weak effects and mixed responses among species in the final models (temperature variable group at HKK, precipitation variable group at HF; Figs. `r clim_sens`, `r GLS_HKK`, `r GLS_HF`), *climwin* identified different climate variables and different time windows (e.g., Fig. `r climwin_diffV_diffW`). 
Henceforth, unless otherwise noted, we focus on the climate sensitivities identified with $RW$ as the growth metric and for the full set of cores (*i.e.*, including those for which $DBH$ could not be reconstructed).

```{r , eval=FALSE, echo=FALSE}
## Tallies for the paragraph below (Feb 8)
#BCNM: 1 species with both, 2 with just P
#HKK: 3 species with both, 1 with just T (CHTA)
#SCBI: 11 species with both, 3 with just P (FRNI, FAGR, PIST)
#LDW:  4 species with both,  2  with just P (ACSA, CAOV)
#HF:  4 species with both
#ZOF:  3 species with both
#NIO:  1 species with both
#LT:  2 species with both
#CB:  8 species with both
#SC:  1 species with both
```
Within the context of the GLS model, which tested for first- and negative second- order linear effects of both a precipitation and a temperature variable, both a precipitation and a temperature variable were included in the top model for 80% of site-species combinations (n=37 of 46; Fig. `r clim_sens`). 
There were seven site-species combinations for which only a precipitation term was significant (2 at BCNM, 3 at SCBI, and 2 at LDW), one for which only a temperature term was significant (*Chukrasia tabularis* at HKK), and none with no significant climate responses. 
Precipitation and temperature variables were rarely influential over the same time window (exception: LDW).
Below, we summarize the precipitation and temperature variables included in these models and their direction of response.

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Feb 8)

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Feb 8)
n_spst_DBH_analyzed= 43 # n species with DBH analyzed: 43 (45 - 2: 2 Hansley)
n_spst_RW_DBH_sig=35 #  species with sig first-order linear DBH term
n_spst_RW_DBH_2nd_order=26
n_spst_RW_DBH_2nd_order_neg=21
n_spst_BAI_DBH_best_model=42 #exception: ACRU at HF  
n_spst_BAI_DBH_best_model_pos=40 #exceptions: PIPO at LT (reconstructed DBH down to only 15cm) and PILO at CB (short DBH range on old trees), both neg but not significant
n_spst_BAI_DBH_best_model_2nd=41
n_spst_BAI_DBH_best_model_2nd_neg=40 # exception: PILO at CB
n_spst_dAGB_DBH_best_model=42 # exception: PILO at CB
```

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Feb8)
n_DBHx_analyzed=204 #n rows in climate_interactions_coefficients, excluding Hansley
n_DBHx_analyzed_sig=88
#precip:
n_DBHxP_RW_analyzed= 36
n_DBHxP_RW_sig=16
n_DBHxP_RW_sig_pos=n_DBHxP_RW_sig-4 #(exceptions: BEAL, TSCA, ACRU at HF, AFXY at HKK*) *pos response to precip in current growing season

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Feb8)
n_tested=37 #same for all metrics
n_best_model_RW=30
n_best_model_BAI=32
n_best_model_AGB=30
n_best_model_neg_RW=n_best_model_RW-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB)  90%
n_best_model_neg_BAI=n_best_model_BAI-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90.6%
n_best_model_neg_AGB=n_best_model_AGB-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90%
percent_neg_of_sig_trends="90-91%"
percent_sig_neg_trend_of_analyzed = "73-78%" 
#species consistently independent of year: PIEN and PILO at CB, CHTA at HKK, PIST3 at NM,
